A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}

### 2020-01-29 4_method.tex
reduce overuse of 'Now that' in section 3

\subsection{Beading}\label{sec_peripheral_height_adjustment}
Now that we have determined the bead counts in the \revise{}{marked }central regions we will describe how the \revise{peripheral}{unmarked} regions are handled.
Determining bead count values for the unmarked nodes and interpolating linearly along the unmarked edges would mean that toolpath sites would be distributed evenly along each unmarked bone;
while that would suffice for the evenly distributed beading scheme, it wouldn't allow for more sophisticated, non-linear schemes.
Instead we determine the radial distance to the boundary at which each bead should occur from the boundary to the center.
Each central node is associated with a sequence of radial distances $L$ which control the locations of the beads, starting from the outer bead and ending in the center.
Together with a sequence of bead widths $W$\revise{}{,} these form what we call a \emph{beading} $B$.
For our distributed beading scheme we compute the beading for a central node $v$ with $n = \lfloor \hat{b}_v \rfloor$ beads and a diameter $r = R(v)$  as:
\begin{align*}
    B(n,r) &= \left( W(n,r), L(n,r) \right)   &=   \left( \left\{  w_0  \dots w_{\lceil n/2 \rceil-1} \right\}, \left\{ l_0 \dots l_{\lceil n/2 \rceil-1} \right\} \right) \\
    w_i &= r / n  & \text{for all $i \in \mathbb{N} : i < n / 2 $}\\
    l_i &= r / n (i + \nicefrac12) & \text{for all $i \in \mathbb{N} : i < n / 2 $}
\end{align*}
where
$w_i$ and $l_i$ are the width and location of the $i$th bead,
respectively, counting from the outline inward.
Example beadings for an odd and even bead count with arbitrary widths are visualized in \cref{example_beading}.

@@

\subsection{Toolpath extraction}\label{sec_toolpath_extraction}
Now that each node has been assigned a beading we proceed to generate the toolpath sites along the edges of the ST.
A site $S$ consists of a location $v$ a width $w$ and an index $i$, which are computed for an edge $v_0v_1$ from the beading $B$ of the upper node $v_1$:
\begin{align*}
S &= \{ v, w, i \} \\ 
v &= v_1 + (v_0 - v_1) \frac{R(v_1) - l_i^B}{R(v_1) - R(v_0)} \\ 
w &= w_i^B
% \\ i^S &= i
\end{align*}
for any $i$ for which $R(v_0) < l_i^B \leq R(v_1)$.
See \cref{site_placement}.
We store all sites of an edge in a mapping from edge to a list of sites.

>>>>

\subsection{Beading}\label{sec_peripheral_height_adjustment}
Now that we \revise{have determined}{know how to determine} the bead counts in the \revise{}{marked }central regions \revise{we will describe}{the question is} how the \revise{peripheral}{unmarked} regions are handled.
Determining bead count values for the unmarked nodes and interpolating linearly along the unmarked edges would mean that toolpath sites would be distributed evenly along each unmarked bone;
while that would suffice for the evenly distributed beading scheme, it wouldn't allow for more sophisticated, non-linear schemes.
Instead we determine the radial distance to the boundary at which each bead should occur from the boundary to the center.
Each central node is associated with a sequence of radial distances $L$ which control the locations of the beads, starting from the outer bead and ending in the center.
Together with a sequence of bead widths $W$\revise{}{,} these form what we call a \emph{beading} $B$.
For our distributed beading scheme we compute the beading for a central node $v$ with $n = \lfloor \hat{b}_v \rfloor$ beads and a diameter $r = R(v)$  as:
\begin{align*}
    B(n,r) &= \left( W(n,r), L(n,r) \right)   &=   \left( \left\{  w_0  \dots w_{\lceil n/2 \rceil-1} \right\}, \left\{ l_0 \dots l_{\lceil n/2 \rceil-1} \right\} \right) \\
    w_i &= r / n  & \text{for all $i \in \mathbb{N} : i < n / 2 $}\\
    l_i &= r / n (i + \nicefrac12) & \text{for all $i \in \mathbb{N} : i < n / 2 $}
\end{align*}
where
$w_i$ and $l_i$ are the width and location of the $i$th bead,
respectively, counting from the outline inward.
Example beadings for an odd and even bead count with arbitrary widths are visualized in \cref{example_beading}.

@@

\subsection{Toolpath extraction}\label{sec_toolpath_extraction}
\revise{Now that}{Once} each node has been assigned a beading\revise{}{,} we proceed to generate the toolpath sites along the edges of the ST.
A site $S$ consists of a location $v$ a width $w$ and an index $i$, which are computed for an edge $v_0v_1$ from the beading $B$ of the upper node $v_1$:
\begin{align*}
S &= \{ v, w, i \} \\ 
v &= v_1 + (v_0 - v_1) \frac{R(v_1) - l_i^B}{R(v_1) - R(v_0)} \\ 
w &= w_i^B
% \\ i^S &= i
\end{align*}
for any $i$ for which $R(v_0) < l_i^B \leq R(v_1)$.
See \cref{site_placement}.
We store all sites of an edge in a mapping from edge to a list of sites.
